Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-03-08 doc/network.tex
updates

@@

>>>>

\section{Example: Middle East Respiratory Syndrome Coronavirus (MERS-CoV)}

\swp{This entire section is missing citations}

We revisit Middle East Respiratory Syndrome Coronavirus (MERS-Cov) outbreak from South Korea in 2015 to explore ideas presented in this study \citep{cowling2015preliminary}. 
The epidemic is characterized by intra- and inter-hospital transmission events and a few super spreading events. 
We expect this kind of scenario to provide a realistic example of an epidemic on a network where we can observe spatial effects on multiple scales (e.g., stronger local depletion effect in intra-hospital transmission than in inter-hosptial transmission).
The data was obtained from the R package \texttt{outbreaks} \citep{outbreakspackage}.
\swp{"This dataset is meant for teaching purposes; it represents neither the final outbreak investigation results nor a consolidated and complete description of the transmission chain." This is what the description says. Is this OK?}

@@

Estimating reproductive number based on generation-interval distributions
